%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{tabularx}

\usepackage{xstring}
\usepackage{xcolor}

\newcommand{\FirstLetterBoldRed}[1]{%
  \StrLeft{#1}{1}[\firstletter]%
  \StrGobbleLeft{#1}{1}[\restletters]%
  {\bfseries\textcolor{red}{\firstletter}}\restletters
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{\FirstLetterBoldRed}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\courseitem}[2]{%
  \item #1 \hfill {\small #2}%
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/rujhanarora/}{\Large Izzy Pasandi}} & Email : \href{mailto:iz.quinz23@gmail.com}{iz.quinz23@gmail.com}\\
  \href{https://www.linkedin.com/in/ipasandi/}{{https://www.linkedin.com/in/ipasandi/}} & Mobile : +1(613)716-9060 \\
\end{tabular*}


%-----------Research Interests-----------------
\section{Research Interests}
\begin{tabular}{p{0.47\textwidth} p{0.47\textwidth}}
  \textsc{Object Recognition} & \textsc{Machine Learning} \\
  \textsc{Computer Vision}  & \textsc{Signal \& Image Processing} \\
  \textsc{Computer Networks} & \textsc{Distributed Real-Time Processing} \\
\end{tabular}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ottawa}{Ottawa, ON}
      {Master of Applied Science (M.A.Sc.), Electrical and Computer Engineering;  \textbf{GPA: 4.0/4.0}}{Nov 2012 – May 2014}
      \resumeItemListStart
        \resumeItem{Thesis} {Face, Age, and Gender Recognition using Local Descriptors}
        \resumeItem{Supervisor}{Prof. Robert Laganière}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharif University of Technology}{Tehran, Iran}
      {Bachelor of Science (B.Sc.), Computer Engineering;  \textbf{GPA: 15.56/20}}{Sep 2006 – May 2011}
      \resumeItemListStart
        \resumeItem{Thesis} {Sparse Representation Techniques for Neighborhood Graph Construction in Pattern Classification}
        \resumeItem{Advisor}{Prof. Afshin Hemmatyar}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------Publication-----------------
\section{Publication}
       	 \resumeSubHeadingListStart
        		\item{E. Fazl-Ersi, Pasandi, R. Laganiere, and M. Awad. Age and gender recognition using informative features of various types. ICIP 2014, pp. 5891–5895.}
	 \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming \& Data Tools}{C, C++, Python, Bash, SQL/NoSQL, OpenCV, MATLAB, LIBSVM}
      
     \resumeSubItem{Distributed Systems \& Cloud}{REST APIs, Microservices, Docker, Kubernetes, Redis, Pub/Sub, GCP, Azure}
      
     \resumeSubItem{Tools \& Practices}{Git, Jenkins, Jira, Confluence, Agile development}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Various Clients(Telnyx Inc., B1 Studio)}{Vancouver, BC}
      {Freelance Software Engineer}{Mar 2023 – Present}
      \resumeItemListStart
      \item
            {Reimplemented and optimized a FreeSWITCH-based real-time voice transcription module for  \textbf{Telnyx}, improving concurrency performance and reducing latency under concurrent workloads.}
       \item
          {Diagnosed and resolved audio pipeline issues (buffer overflows, memory leaks) for  \textbf{Telnyx}, enhancing reliability in high-volume distributed call environments.}
        \item
          {Built automation and tooling to streamline operational workflows for client support at \textbf{B1 studio}, streamlining internal operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Dialpad}{Vancouver, BC}
      {Senior Software Engineer I}{Aug 2021 – Feb 2023}
      \resumeItemListStart
        \item
          {Maintained and enhanced real-time comms microservices (Plivo, FreeSWITCH) in C/C++ and Python.}
        \item
          {Designed and implemented a pub/sub–based call-quality monitoring system enabling live feedback across distributed services.}
        \item{Debugged network signalling and RTP media pipelines to ensure low-latency and fault-tolerant operation.}
        \item{Participated in the migration of legacy Python 2.7 systems to version 3.5 as part of a collaborative team, while enhancing unit testing coverage.}
         \item{Supported customers by investigating GCP production issues, performing distributed debugging across Pub/Sub pipelines, Bigtable storage layers, and Cloud Functions execution paths.}
      \resumeItemListEnd
      
      
          \resumeSubheading
      {Ciena Corporation}{Ottawa, ON}
      {Embedded Software Engineer II}{Jun 2015 – Jun 2021}
      \resumeItemListStart
        \item{Developed signal–loss diagnostics microservice in C++, improving diagnostic accuracy and reducing troubleshooting time.}
        \item{Implemented automated topology discovery for large-scale submarine FlexGrid networks.}
        \item{Enhanced reliability and fault-detection modules for carrier-grade transport products.}
         \item{Used Bash and Python scripting extensively for automation, observability, deployment tooling, and performance monitoring.}
      \resumeItemListEnd
      
      
      \resumeSubheading
      {ADitude Media Corporation}{Ottawa, ON}
      {Software Engineer}{Sep 2014 – Jun 2015}
      \resumeItemListStart
        \item
          {Integrated a set of Ad networks with proprietary computer vision software for targeted media delivery.}
        \item
          {Optimized image-processing pipelines for real-time face detection and recognition in production environments.}
      \resumeItemListEnd
      
          \resumeSubheading
      {VIVA Lab, University of Ottawa}{Ottawa, ON}
      {Research Assistant}{Nov 2012 – Jul 2014}
      \resumeItemListStart
        \item{Designed and implemented a real-time facial analysis application capable of high-accuracy age \& gender estimation.}
        \item{Applied machine learning and local descriptor–based methods for face analysis under constrained compute resources.}
        \item{Conducted experimental evaluation, feature extraction, and performance optimization for real-time vision algorithms.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Teaching Assistant}
  \resumeSubHeadingListStart
    \resumeSubItem{Sharif University of Technology}{}

\resumeItemListStart
  \courseitem{Electrical Circuits}{Fall 2008, Spring 2009}
  \courseitem{Introduction to Programming}{Fall 2008}
  \courseitem{Signals \& Systems}{Spring 2010}
  \courseitem{Linear Control Systems}{Spring 2010}
  \courseitem{Probability \& Statistics}{Fall 2010}
\resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Volunteer \& Community Engagement}
  \resumeSubHeadingListStart
  \resumeItemListStart
    \item{Co-facilitated a local peer support group at Qmunity, contributing to inclusive community wellbeing and providing weekly guidance to participants.}
    \item{Volunteer contributor at a local community spirit fair (2023–present), supporting event operations and outreach.}
    \item{Led guided sea-kayaking tours at Jericho Kayaking Centre, ensuring group safety, navigation, and positive participant experiences.}
    \item{Certified Level 3 Sea Kayaker, demonstrating advanced skills, safety training, and outdoor leadership.}
    \resumeItemListEnd
       \resumeSubHeadingListEnd
 
%-------------------------------------------
\end{document}